Ripple Consensus Review

### 2015-04-21 paper.tex
checkpoint

@@

>>>>

Claims from ripple: consensus protocol will maintain correctness so long as $f
\le (n-1)/5$ where $f$ is the number of Byzantian failures. However default UNL
list is just $5$ entries, thus $f \le (5-1)/5 = 0.8$ - no failures can be
tolerated.

Put antoher way, you only need to compromise $20\%$ of the nodes in the UNL to
censor a transactions/freeze funds. "failure to agree is agreement to defer"

Is there incentive to use anything but the default UNL? Remember that if you
choose a UNL more than $80\%$ different than others, you can be attacked on
that basis; your full node determines validity of transactions anyway. e.g. the
"add 1000 validators to UNL list" suggestion.

mixing structure: if tx A is rejected, dependent txs are all rejected; will
likely soon result in situation where you can't use different UNL

@@

test: add extra entries to UNL list, see if ledgers close, if they don't think we know threshold
